---
output: github_document
---

# survdistr

Survival distribution container for efficient storage, management, and interpolation of survival model predictions.

<!-- badges: start -->
[![r-cmd-check](https://github.com/mlr-org/survdistr/actions/workflows/r-cmd-check.yml/badge.svg)](https://github.com/mlr-org/mlr3survival/actions/workflows/r-cmd-check.yml)
[![Codecov test coverage](https://codecov.io/gh/mlr-org/survdistr/branch/main/graph/badge.svg)](https://app.codecov.io/gh/mlr-org/survdistr?branch=main)
<!--[![CRAN Status](https://www.r-pkg.org/badges/version-ago/survdistr)](https://cran.r-project.org/package=survdistr) -->
<!-- badges: end -->

## Installation

Install the development version from GitHub:

```{r eval = FALSE}
# install.packages("pak")
pak::pak("mlr-org/survdistr")
```

## Examples

Linear interpolation of a survival matrix using the `survDistr` R6 class:
```{r}
library(survdistr)

# generate survival matrix
mat = matrix(data = c(0.9,0.6,0.4,0.8,0.8,0.7), nrow = 2,
             ncol = 3, byrow = TRUE)
x = survDistr$new(x = mat, times = c(12, 34, 42), method = "linear_surv")
x

# stored survival matrix
x$data()

# S(t) at requested time points (linear interpolation)
x$survival(times = c(5, 30, 42, 50))

# Cumulative hazard H(t)
x$cumhazard(times = c(5, 42))

# Probability density f(t)
x$density(times = c(5, 30, 42))

# Hazard h(t)
x$hazard(times = c(5, 30, 42))
```

Interpolation of a Kaplan-Meier survival curve using exported R function that calls C++ code:
```{r}
library(survival)

fit = survfit(formula = Surv(time, status) ~ 1, data = veteran)
tab = data.frame(time = fit$time, surv = fit$surv)
head(tab)
tail(tab)

# constant S(t) interpolation
interp(
  x = tab$surv,
  times = tab$time,
  eval_times = c(0, 3.5, 995)
)

# linear S(t) interpolation
interp(
  x = tab$surv,
  times = tab$time,
  eval_times = c(0, 3.5, 995),
  method = "linear_surv"
)

# exponential S(t) interpolation
interp(
  x = tab$surv,
  times = tab$time,
  eval_times = c(0, 3.5, 995),
  method = "exp_surv"
)
```

## Code of Conduct

Please note that the survdistr project is released with a [Contributor Code of Conduct](https://survdistr.mlr-org.com/CODE_OF_CONDUCT.html).
By contributing to this project, you agree to abide by its terms.
